---
title: "Juliette HW 1"
author: "Juliette J. Rubin"
date: "January 23, 2019"
output: pdf_document
---

```{r setup, include=FALSE}

library("knitr")
library("bookdown")
library("knitcitations")

knitr::opts_chunk$set(echo = TRUE)
## Text results
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, tidy.opts = list(blank = TRUE, width.cutoff = 80), highlight = TRUE)

## Plots
opts_chunk$set(fig.path = "figures/", dev=c('pdf', 'png'), dpi = 300)
```

## Question 1
Math scores and LSD

```{r math, results='asis'}

math<-read.csv("math_scores.csv")
model1<-lm(math$MATH_score~math$LSD_concentration)
coef(model1)
confint(model1)

#finding model fit
#create vector of predictions
yhat<-89.12+(-9.009)*math$LSD_concentration
#calculate SS
mean_score<-mean(math$MATH_score)
SS<-sum((math$MATH_score-mean_score)^2)
#calculate RSS
RSS<-sum((math$MATH_score-yhat)^2)
#calculate R squared
(SS-RSS)/SS

#trying model fit with the given functions, but it isn't providing an output?
yhat<-89.12+(-9.009)*math$LSD_concentration
y<- math$MATH_score

r2<-function(y_hat,y) { 
  RSS<-sum((((y_hat))-(y))^2) 
  TSS<-sum(((y)-(mean(y)))^2) 
  return(1-RSS/TSS)} 


rmse=function(y_hat,y) { 
  return(sqrt(mean((y-y_hat)^2))) 
}
```
We find that the equation of this line is comprised of the following values: Intercept = 89.12, Slope=-9.009 and the metric of model fit as determined by our functions above is R^2=0.878. Additionally, our confidence interval output indicates that there is a sig effect of LSD concentration on math scores, as 95% of the time we are going to get an effect of LSD on math scores.

1B) Although our math score data seems to be tightly associated with LSD intake, we can't say much about its predictive qualities because r^2 says little about prediction error, and thus we could be wrong

1C) The normal distribution might not be acceptable for these data because grades do not go to positive and negative infinity. There are set bookends.

```{r equation 1A}

#y=mx+b
(85-89.12)/-9.009

#result = 0.46 LSD concentration

```

### Math score plot


```{r mathplot, echo=TRUE}

plot(mathscore$MATH_score~mathscore$LSD_concentration)
curve(89.12+(-9.009)*x, add=T, col="blue")

```

##Question 2 

Pomegranate miracle food

```{r pomegranate}

miracle<-read.csv("miracle_food.csv")
model2<- lm(miracle$Weight_loss~miracle$pomegranate)
coef(model2)
confint(model2)

yhat<--0.179+(-0.525)*miracle$pomegranate
#calculate SS
mean_Weightloss<-mean(miracle$Weight_loss)
SS<-sum((miracle$Weight_loss-mean_Weightloss)^2)
#calculate RSS
RSS<-sum((miracle$Weight_loss-yhat)^2)
#calculate R squared
(SS-RSS)/SS

#r^2 = 0.008

```

We find that the equation of this line is comprised of the following values: intercept=-0.179, slope=-0.525. Our confidence intervals do not indicate that this is a significant effect and our r^2 value is quite low, meaning that our model is worse than just assessing mean weight loss. I therefore cannot agree with the farmer's claim (though I don't dismiss its efficacy as an ad campaign).


```{r pom plot}

plot(miracle$Weight_loss~miracle$pomegranate)
curve(-0.179+(-0.525*x),add=T, col="red")

```



##Question 3

```{r}

#Trying a fancy way...
for (i in 1:length(dataset)){
  MAE<-function(y_hat,y){
    absdif<-abs(y[i]-y_hat)
    sums<-sum(absdif)
    return(sums/n)
  }
  
}

#OK this is the real one (MATH) -- none of my functions are outputting results!
yhat<-89.12+(-9.009)*math$LSD_concentration
y<- math$MATH_score
n<-7
MAE<-function(y_hat,y){
  absdif<-abs(y-y_hat)
  return((sum(absdif))/n)
}

#MIRACLE
yhat<--0.179+(-0.525)*miracle$pomegranate
y<- miracle$Weight_loss
n<-7
MAE<-function(y_hat,y){
  absdif<-abs(y-y_hat)
  return((sum(absdif))/n)
}





```

##Question 4

```{r pubs}

days_skiing<-runif(100)
slope<--0.4
intercept<-2
sigma<-0.8
publications<- rnorm(n=100, mean= intercept + slope*days_skiing, sd=0.8)
publications

model3<- lm(publications~days_skiing)
coef(model3)
confint(model3)

plot(publications~days_skiing)
curve(1.834+(-0.26*x),add=T, col="green")


```


When trying to assess how the number of days a person goes skiing in a year affects the number of publications the person submits that year, we find that the equations of the line is y=-0.26*days-skiing + 1.834. This is different from the true values that I came up with, presumably due to the variance introduced into this dataset with a sd of 0.8


##Question 5

```{r equation}

congress_days<-runif(100)
slope<-0.7
intercept<-10
sigma<-.5*congress_days
bills_passed<- rnorm(n=100, mean= intercept + slope*congress_days, sd=sigma)

plot(bills_passed~congress_days)
```

This would indicate that the more days congress spends in session the more variable it becomes whether they do their jobs and pass legislature (let alone what the content of those bills are), or whether the environment becomes too acerbic to get anything done.

